Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-24 scripts/03_clustering.Rmd
Stability measures for clustering & all

# Rescale the centroids
centroids = moanin:::rescale_values(kmeans_clusters$centroids, splines_model)

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=as.vector(unlist(ann_colors["Group"])),
			smooth=FALSE)
```

@@

>>>>

# Rescale the centroids
centroids = moanin:::rescale_values(kmeans_clusters$centroids)

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, splines_model,
			colors=ann_colors$Group,
			smooth=TRUE)
```

Now, let's look at genes in cluster 15

```{r fig.width=8, fig.height=8}
gene_names = row.names(data)
genes_to_plot =  names(kmeans_clusters$clusters[kmeans_clusters$clusters == 15])
data_to_plot = data[genes_to_plot, ]
submeta = meta
submeta$Group = factor(submeta$Group, levels(submeta$Group)[c(3, 1, 2, 5, 4)])
ord = order(
  submeta$Group,
  submeta$Timepoint,
  submeta$Replicate)
submeta$Timepoint = as.factor(submeta$Timepoint)

data_to_plot = data_to_plot[, ord]
submeta = submeta[ord, ]

NMF::aheatmap(
    data_to_plot,
    Colv=NA,
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main="Cluster 15",
    treeheight=0)

NMF::aheatmap(
    moanin:::rescale_values(data_to_plot),
    Colv=NA,
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main="Cluster 15",
    treeheight=0)

@@

### Looking at the stability of the clustering

```{r fig.width=6, fig.height=4}
library(NMF)
stability_5 = read.table("results/stability_5.tsv", sep="\t")
consensus_matrix_stability_5 = moanin::consensus_matrix(stability_5,
							scale=FALSE)
NMF::aheatmap(consensus_matrix_stability_5[1:1000, 1:1000], Rowv=FALSE,
	      Colv=FALSE,
	      treeheight=0)

stability_20 = read.table("results/stability_15.tsv", sep="\t")
consensus_matrix_stability_20 = moanin::consensus_matrix(stability_20,
							 scale=FALSE)
NMF::aheatmap(consensus_matrix_stability_20[1:1000, 1:1000], Rowv=FALSE,
	      Colv=FALSE,
	      treeheight=0)
